\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[margin=0.75in]{geometry} % Replaced fullpage with geometry
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.375in}
% \addtolength{\evensidemargin}{-0.375in}
% \addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://alok92.github.io/about/}{\Large Alok}} & Email : \href{mailto:alokc24@gmail.com}{alokc24@gmail.com}\\
  \href{https://www.linkedin.com/in/alok92/}{https://www.linkedin.com/in/alok92/} & Mobile : +91-91761-45275 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Flipkart}{Bangalore}
      {Senior Site Reliability Engineer}{Dec 2022 - Present}
      \resumeItemListStart
        \resumeItem{Event-Driven Automation}
          {Spearheaded adoption of StackStorm for event-driven automation across multiple orgs, leading a blended team of 5 and reducing manual intervention in operational workflows by 65\%, significantly improving incident response and engineering efficiency.}
        \resumeItem{VM Service Catalog}
          {Architected and delivered a high-scale VM Service Catalog leveraging SaltStack, enabling orchestration across 30,000 servers in under one second and standardizing VM provisioning for platform-wide use.}
        \resumeItem{Codelift}
          {Leading a team of 6 engineers to build "Codelift," a scalable internal developer platform automating mass codebase and runtime upgrades (e.g., JDK, libraries), achieving a current success rate of 53\% and reducing manual upgrade cycles org-wide.}
        \resumeItem{Eventstore Platform}
          {(Early stages)Driving strategy and technical direction for a unified observability platform (Eventstore), collaborating with 10 senior engineers across teams to consolidate distributed tracing, service graphs, logging, and change intelligence into a single pane of glass.}
      \resumeItemListEnd

    \resumeSubheading
      {Yugabyte}{Bangalore}
      {Site Reliability Engineer/Manager}{June 2022 - Dec 2022}
      \resumeItemListStart
        \resumeItem{Secret Management}
          {Led the org-wide migration of sensitive secrets to a centralized, secure vault-backed solution, achieving 100\% adoption across the organization, enhancing compliance and reducing security vulnerabilities by standardizing secret access and lifecycle management.}
        \resumeItem{Test Coverage}
          {Drove a quality-first initiative to uplift test coverage from 19\% to 65\% across critical services, embedding linting and testing into CI/CD pipelines and improving deployment confidence at scale.}
      \resumeItemListEnd

    \resumeSubheading
      {Arcesium}{Bangalore}
      {Reliability Engineering Lead/Manager}{Mar 2021 - June 2022}
      \resumeItemListStart
        \resumeItem{Hiring and Training}
          {Built and scaled a high-performing SRE team (2 Tech Leads, 7 SREs). Owned recruitment, onboarding, and ongoing mentorship, including performance management and career development plans—resulting in 4 internal promotions and significantly improved retention.}
        \resumeItem{Incident Management Bot}
          {Designed and implemented an Incident Management bot using Opsdroid, achieving 100\% adoption within 4 months and reducing toil in on-call workflows by over 70\%, aligning with SRE best practices for automation.}
        \resumeItem{SLI/SLO}
          {Led org-wide adoption of SLI/SLO practices, onboarding 30\% of teams in 90 days. Partnered with Engineering and Product to align reliability goals with OKRs, while coaching teams on operational maturity and long-term planning.}
        \resumeItem{Team Strategy \& Execution}
          {Led team-level sprint execution, backlog grooming, and velocity tracking. Conducted regular 1:1s, performance evaluations, and growth check-ins, aligning individual development with team and org-level goals.}
        
      \resumeItemListEnd

    \resumeSubheading
      {Expedia}{Gurgaon/Bangalore}
      {Software Development Engineer/Lead SRE}{Oct 2015 - Oct 2020}
      \resumeItemListStart
        \resumeItem{Sponsored Listing}
          {Led the design and launch of a high-impact Sponsored Listings ad product, driving multi-million dollar revenue with a 6\% conversion rate.}
        \resumeItem{Notification Delivery Platform}
          {Collaborated with another team to develop a notification delivery platform, integrating it into the organization's wide CI/CD pipelines as the standard.}
        \resumeItem{Logging \& Monitoring Framework}
          {Led a team of 5 to develop an end-to-end logging and monitoring framework, reducing Mean Time To Detection (MTTD) by 80\%, resulting in \$2-3 million USD per year in cost savings, and contributing to a significant reduction in overall downtime}
        \resumeItem{Operations to SRE transition}
          {Pioneered a cross-functional upskilling initiative that transitioned 10 operations analysts into fully functional SREs, enhancing team capabilities while fostering a strong DevOps culture.}
        \resumeItem{Change Management System}
          {Developed a change management system integrated with ServiceNow, capturing over 95\% of platform changes for enhanced traceability.}
        \resumeItem{People \& Sprint Leadership}
          {Owned sprint ceremonies (planning, grooming, retrospectives) and quarterly team goals. Conducted performance reviews, drove individual development plans, and mentored junior engineers across SRE tracks.}
        
      \resumeItemListEnd

    \resumeSubheading
      {TCS}{Chennai}
      {Systems Engineer}{Sep 2014 - Sep 2015}
      \resumeItemListStart
        \resumeItem{Bill Generator}
          {Created Windows-based UI for users to work on the risk files, update databases \& generate billing information for auto insurance which eliminated human errors completely.}
      \resumeItemListEnd

    \resumeSubheading
      {Airtkt}{Delhi}
      {Web Developer}{Feb 2014 - Aug 2014}
      \resumeItemListStart
        \resumeItem{Search Filters \& Notifications}
          {Added flight search filters to Airtkt.com for better customer experience \& implemented a near real-time notification service for the support team}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{T-Rex}
      {\href{https://alok92.github.io/t-rex/}{My version of Chrome T-rex game using JavaScript and Image Sprites.}}
    \resumeSubItem{Tweetcheat}
      {Using Tweepy, Tweetcheat parses tweets containing certain texts and then retweets/favorites them to win gifts/coupons}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Languages}{: Python, JavaScript, Bash} \\
      \textbf{Markup \& Configuration Languages}{: HTML, CSS, JSON, YAML} \\
      \textbf{Frameworks \& Backends}{: Node.js, Flask} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, PyCharm, IntelliJ, VIM, ServiceNow} \\
     \textbf{Cloud \& Infrastructure}{: AWS, GCP, Terraform, CloudFormation, Ansible} \\
     \textbf{Databases}{: MySQL, PostgreSQL, MongoDB} \\
     \textbf{Monitoring \& Observability}{: Datadog, Prometheus, Grafana, Splunk, Kibana, Catchpoint} \\
     \textbf{Containers \& Orchestration}{: Docker, Kubernetes, Helm} \\
     \textbf{CI/CD \& Automation}{: Jenkins, ArgoCD, GitLab CI/CD, StackStorm, SaltStack} \\
     \textbf{Logging \& Message Brokers}{: Elasticsearch, Kafka, Zookeeper} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
